\texttt Design date

### 2017-04-13 latex/keyexchange/secretkeybasedpublickeyencryption.tex
noted ability to re-use RSA keypairs

\author{Anonymous\inst{1}}
\institute{City, State \email{address@provider.com}}
\title[\texttt Design date]{\texttt Design date}

@@

\begin{abstract}
  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas. The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\ 
\end{abstract}

@@

\subsection{Key Exchange Algorithm}
Let $pb_1$ and $pb_2$ be two encryptions of $0$ under the homomorphic secret key cipher. These two values constitute a public key. To share a secret with the owner of the public key, compute:
\begin{align}
    e \gets secret \\
    c \gets (pb_1  r_1) + (pb_2 r_2) + e
\end{align}

Then the value $c$ is shared with the owner of the public key. The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $pb_1$ is an encryption of $0$, $pb_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $pb_2$. So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.

\subsection{Secret Key Cipher}
Creation of the $pb_1$ and $pb_2$ values requires a secure, additively homomorphic cipher. We define a simple lattice based cipher which utilizes effectively the same operations as the key exchange process. Let $p_1$ and $p_2$ be two large numbers, where $log_2(p_1) >= log_2(p_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\

@@

\begin{align}
   c \gets (p_1 r_1) + (p_2 r_2) + m
\end{align}

Where the $r$ values are of appropriate size relative to $p_1$ and $p_2$ \todo{what sizes are appropriate}
While decryption is computed as:

\begin{align}
    m \gets (c \mod p_1) \mod p_2
\end{align}

@@

\section{Conclusion}
 We define a simple lattice based key exchange algorithm. The algorithm utilizes 2 bignum multiplications and 2 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key. Public keys typically occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
\end{document}

>>>>

\author{Ella Rose\inst{1}}
\institute{Paso Robles, CA \email{address@provider.com}}
\title[\texttt Design date]{\texttt Design date}

@@

\begin{abstract}
  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas. The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple. Additionally, it is possible to utilize pre-existing RSA keypairs to perform the exchange. While doing so does not increase security beyond that of regular RSA, it is much faster.\\ 
\end{abstract}

@@

\subsection{Key Exchange Algorithm}
Let $p_1$ and $p_2$ be two encryptions of $0$ under the homomorphic secret key cipher. These two values constitute a public key. To share a secret with the owner of the public key, compute:
\begin{align}
    e \gets secret \\
    c \gets (p_1  r_1) + (p_2 r_2) + e
\end{align}

Then the value $c$ is shared with the owner of the public key. The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $p_1$ is an encryption of $0$, $p_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $p_2$. So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.

\subsection{Secret Key Cipher}
Creation of the $p_1$ and $p_2$ values requires a secure, additively homomorphic cipher. We define a simple lattice based cipher which utilizes effectively the same operations as the key exchange process. Let $s_1$ and $s_2$ be two large numbers, where $log_2(s_1) >= log_2(s_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\

@@

\begin{align}
   c \gets (s_1 r_1) + (s_2 r_2) + m
\end{align}

Where the $r$ values are of appropriate size relative to $s_1$ and $s_2$ \todo{what sizes are appropriate}
While decryption is computed as:

\begin{align}
    m \gets (c \mod s_1) \mod s_2
\end{align}

@@

\subsection{Re-using RSA keypairs for the exchange}
An RSA modulus can be used as a public key for the exchange presented previously; Simply substitute the RSA public key $n$ in place of the points $p_1$ and $p_2$, and modify the decryption algorithm to utilize a single modulo $p$ (as in the $p$ from $pq == n$). While this does not offer a security advantage to regular RSA encryption (here we offer no proof of security of any kind), it is significantly faster. Performing 1024 key exchanges using naive/textbook RSA-2048 requires approximately 1 second on our test machine; Performing 1024 key exchanges using the RSA-Lattice technique requires about .25 seconds on our test machine. This is largely the result of not needing to perform modular exponentiation with the lattice based technique.

\section{Conclusion}
 We define a simple lattice based key exchange algorithm. The algorithm utilizes 4 bignum multiplications and 4 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key. Public keys occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits. Interestingly, pre-existing RSA keypairs may be used to instantiate the shceme.
\end{document}
